censusprocessing

### 2021-11-02 code/processing_code/censusland_code.Rmd
add API key, remove incorrect files
added API key to censusprocessing.Rmd to attempt to fix run error

##Load Census API (load only once)
```{r}
#specify from which package a function is to be used

#tidycensus::census_api_key("c02ef0638e60f9d5fbb45de5219821e3a25cd7d2", install = TRUE) 
```
^This is not a code chunk you will need in every notebook. As long as "install = TRUE", you will only have to do this once. 
#restart R session after installing the first time

>>>>

##Load Census API (load only once)
```{r}
#tidycensus::census_api_key("c02ef0638e60f9d5fbb45de5219821e3a25cd7d2", install = TRUE) 
```
^This is not a code chunk you will need in every notebook. As long as "install = TRUE", you will only have to do this once. 
#restart R session after installing the first time

### 2021-11-02 code/processing_code/censusprocessing.Rmd
add API key, remove incorrect files
added API key to censusprocessing.Rmd to attempt to fix run error

I am realizing that we can get more localized population levels by using census tracts, which are smaller levels of census geography. Let's try to use FIPS codes (which include tract info) to obtain population data that might be more informative. 
# Converting coordinates to FIPS
```{r}
#create function
latlong2fips <- function(latitude, longitude) {
  url <- "https://geo.fcc.gov/api/census/block/find?format=json&latitude=%f&longitude=%f"
  url <- sprintf(url, latitude, longitude)
  json <- RCurl::getURL(url)
  json <- RJSONIO::fromJSON(json)
  as.character(json$Block['FIPS'])
}
#vectorize so function will take more than one argument
latlong2fips_vec <- Vectorize(latlong2fips, vectorize.args = "latitude", "longitude")

>>>>

I am realizing that we can get more localized population levels by using census tracts, which are smaller levels of census geography. Let's try to use FIPS codes (which include tract info) to obtain population data that might be more informative. 
# Converting coordinates to FIPS
```{r}
#load census API key
tidycensus::census_api_key("c02ef0638e60f9d5fbb45de5219821e3a25cd7d2", install = TRUE, overwrite = TRUE)

#create function
latlong2fips <- function(latitude, longitude) {
  url <- "https://geo.fcc.gov/api/census/block/find?format=json&latitude=%f&longitude=%f"
  url <- sprintf(url, latitude, longitude)
  json <- RCurl::getURL(url)
  json <- RJSONIO::fromJSON(json)
  as.character(json$Block['FIPS'])
}
#vectorize so function will take more than one argument
latlong2fips_vec <- Vectorize(latlong2fips, vectorize.args = "latitude", "longitude")
